Parameter Inference\\with Bifurcation Diagrams

### 2021-05-22 docs/appendix.tex
Updates from Overleaf

An expression for the field $\tangent(z)$ tangent to the set of curves would allow us to take derivatives and integrals along the bifurcation curve. This is exactly what we need to do to evaluate our cost function \ref{eq:cost}. Fortunately the tangent field can be constructed by ensuring it is perpendicular to the gradient $\partial_z$ of each component of $\rates$ as illustrated by an example two component system in Figure \ref{fig:implicit-surfaces}. The tangent field $\tangent(z)$ can be constructed perpendicular to all gradient vectors using the properties of the determinant \cite{Goldman2005CurvatureSurfaces}

@@

\section{Simplification of two-state model}

Consider the general two-state model:
\begin{equation}
    \dfrac{dv_i}{dt} = \dfrac{a_i + b_i (K_i v_j)^2}{1 + (K_i v_j)^2} - \mu_i v_i
\end{equation}

Without loss of generality, we can rescale $v_i = U_i u_i$. Then,
\begin{equation}
    \dfrac{U_idu_i}{dt} = \dfrac{a_i + b_i (K_i U_j u_j)^2}{1 + (K_i U_j u_j)^2} - \mu_i U_i u_i
\end{equation}

Dividing through by $U_i$, we obtain
\begin{equation}
    \dfrac{du_i}{dt} = \dfrac{\frac{a_i}{U_i} + \frac{b_i}{U_i} (K_i U_j u_j)^2}{1 + (K_i U_j u_j)^2} - \mu_i u_i
\end{equation}

By choosing $U_i = b_i$, the model reduces to:
\begin{equation}
    \dfrac{du_1}{dt} = \dfrac{\hat{a}_1 + (p u_2)^2}{1 + (p u_2)^2} - \mu_1 u_1, \quad
    \dfrac{du_2}{dt} = \dfrac{\hat{a}_2 + (k u_1)^2}{1 + (k u_1)^2} - \mu_2 u_2
\end{equation}
where $p = \frac{K_1}{\sqrt{b_1}}$ and $k = \frac{K_2}{\sqrt{b_2}}$.

>>>>

An expression for the field $\tangent(z)$ tangent to the set of curves would allow us to take derivatives and integrals along the bifurcation curve. This is exactly what we need to do to evaluate our cost function \ref{eq:loss}. Fortunately the tangent field can be constructed by ensuring it is perpendicular to the gradient $\partial_z$ of each component of $\rates$ as illustrated by an example two component system in Figure \ref{fig:implicit-surfaces}. The tangent field $\tangent(z)$ can be constructed perpendicular to all gradient vectors using the properties of the determinant \cite{Goldman2005CurvatureSurfaces}

@@

% \section{Simplification of two-state model}

% Consider the general two-state model:
% \begin{equation}
%     \dfrac{dv_i}{dt} = \dfrac{a_i + b_i (K_i v_j)^2}{1 + (K_i v_j)^2} - \mu_i v_i
% \end{equation}

% Without loss of generality, we can rescale $v_i = U_i u_i$. Then,
% \begin{equation}
%     \dfrac{U_idu_i}{dt} = \dfrac{a_i + b_i (K_i U_j u_j)^2}{1 + (K_i U_j u_j)^2} - \mu_i U_i u_i
% \end{equation}

% Dividing through by $U_i$, we obtain
% \begin{equation}
%     \dfrac{du_i}{dt} = \dfrac{\frac{a_i}{U_i} + \frac{b_i}{U_i} (K_i U_j u_j)^2}{1 + (K_i U_j u_j)^2} - \mu_i u_i
% \end{equation}

% By choosing $U_i = b_i$, the model reduces to:
% \begin{equation}
%     \dfrac{du_1}{dt} = \dfrac{\hat{a}_1 + (p u_2)^2}{1 + (p u_2)^2} - \mu_1 u_1, \quad
%     \dfrac{du_2}{dt} = \dfrac{\hat{a}_2 + (k u_1)^2}{1 + (k u_1)^2} - \mu_2 u_2
% \end{equation}
% where $p = \frac{K_1}{\sqrt{b_1}}$ and $k = \frac{K_2}{\sqrt{b_2}}$.
